Supplementary Information

### 2021-08-31 doc/manuscript/response_to_reviews.Rmd

**The key point with the hypotheses referenced is that we hypothesize that "[RW] *initially* increases with DBH for shade-tolerant species." This hypothesis does not preclude a subsequent decline in RW across larger size classes, which indeed was the most common outcome (described in results, "Variation with DBH" section, paragraph starting with "For RW, DBH was included..."). We have carefully reviewed the language around this issue to ensure that descriptions of an "increasing" trend in RW refer only to the smaller end of the DBH range, and have found all of the language to be accurate. While a more thorough investigation of DBH trends in growth rate and their interrelationships across growth metrics could be interesting and informative, this would be beyond the scope of the current paper.**

**More broadly, we believe that the relationships among results for the various growth metrics are fundamentally consistent. We would expect, and observe, some modest differences in climate variables selected (e.g., because the various growth metrics would effectively place different weight on above- or below-average growth rates for large vs small trees), variables included in the best model, etc. However, the results across growth metrics are broadly consistent.**

 L222-224:
Dealing with tree and forest mortality is difficult. However, climate change is predicted to affect mortality in many forests. In turn, mortality can impact the growth of the remaining trees depending on the stature and location of the dead tree. This point should be addressed- the article presents the relationship between growth and climate only for the surviving trees. How does excluding growth data from the analysis potentially bias the results?

**We're not entirely sure how to interpret this comment.**

**If the question is how increasing mortality might impact growth trends with year, increased mortality would result in decreased competition and potential growth release for surviving individuals. Thus, in theory, we might expect increasing mortality rates in many forests around the world [@mcdowell_pervasive_2020] to result in trends of increasing growth. However, mortality trends may not be notable enough at our sites to produce this effect, or may even go in the opposite direction (e.g., reduced intermediate disturbances at CB). Moreover, increased mortality is often correlated with decreased growth unless the conditions reverse (so, for example, the trend at SC is towards increased mortality and decreased growth). Overall, in this analysis, negative growth trends predominate, and so we do not believe that growth release from increasing mortality is a dominant factor. However, we have added mention of changing mortality rates in the discussion: "Within the three older forests (ZOF, LT, CB), population-mean growth trends were mixed (Table 1, Fig. 7), probably reflecting some combination of successional changes, *changing mortality rates*, and shifting competitive advantages, perhaps in part driven by changing environmental conditions [@furniss_reconciling_2017; @vrska_european_2009] or the lack of intermediate disturbances giving rise to increasing crowding [e.g., @lutz_twentiethcentury_2009]."**

**If the question is about differences in climate sensitivity between the trees that die and those that survive, this is an interesting question, but remains beyond the scope of this analysis. For one site where we included cores from trees cored dead and live (SCBI), we previously found that trees cored dead displayed similar climate sensitivity to trees cored live [@helcoski_growing_2019]. Other studies have found differences in drought sensitivity among trees that survived or died during a drought, but even if that occurred at one or more of our sites, it does not seem like it would fundamentally alter any of our results or conclusions.**

### 2021-09-07 doc/manuscript/ForestGEO_treerings.Rmd
add Zenodo DOI
issue #146

Code and full results are available via the open-access project repository in GitHub (https://github.com/EcoClimLab/ForestGEO-tree-rings) and archived in Zenodo (DOI: TBD).
Original data from each site are available through various public databases, as indicated in the original publications, or upon reasonable request from the authors.
Data for *[# TBD]* of the sites are archived in the The DendroEcological Network (DEN) database [SCBI, *[others TBD]*, @rayback_dendroecological_2020] and/or the International Tree-Ring Data Bank, ITRDB (CB).

>>>>

Code and full results are available via the open-access project repository in GitHub (https://github.com/EcoClimLab/ForestGEO-tree-rings) and archived in Zenodo (DOI: 10.5281/zenodo.5484261).
Original data from each site are available through various public databases, as indicated in the original publications, or upon reasonable request from the authors.
Data for *[# TBD]* of the sites are archived in The DendroEcological Network (DEN) database [SCBI, *[others TBD]*, @rayback_dendroecological_2020] and/or the International Tree-Ring Data Bank, ITRDB (CB).
